\huge Tor's Usability for Censorship Circumvention

### 2016-05-05 pets2017-paper/pets2017-paper.tex
add placeholders for active time TODOS

@@

The new interface results a statistically significant reduction in the overall active configuration time (Mann--Whitney $Z = -3.055$, $p = 0.00225$, $r= 0.284$). We believe that getting rid of the technical questions and telling participants that they did not need a proxy attributed to the reduction in time. 
%The impact of the environment on active time is significant (Kruskal--Wallis $\chi^2 = 51.978$, $\mbox{df} = 2$, $p = 10^{-11}$)

>>>>

\begin{table}
\centering
	\begin{tabular}{c r r}
	 & Total Active Minutes & \% of Overall Time \\
	\noalign{\hrule}
	All & 381 & 29\% \\ 
	E1-NEW & 4 & 45\% \\
	E1-OLD & 19 & 67\% \\
	E2-NEW & 15 & 15\% \\
	E2-OLD & 68 & 31\% \\
	E3-NEW & 74 & 18\% \\
	E3-OLD & 200 & 38\% \\
	\end{tabular}
\caption{active time {\color {red} add comparable figure to the time to success figure (Fig 9)}.} 
\label{table:active_time}
\end{table}

@@

{\color {red} TODO: explain how this was calculated: across all participants, with DNF's getting 40:08 then subtracting the time they spent on the progress screen)} The new interface results a statistically significant reduction in the overall active configuration time. (Mann--Whitney $Z = -3.055$, $p = 0.00225$, $r= 0.284$). We believe that getting rid of the technical questions and telling participants that they did not need a proxy attributed to the reduction in time. 
%The impact of the environment on active time is significant (Kruskal--Wallis $\chi^2 = 51.978$, $\mbox{df} = 2$, $p = 10^{-11}$)
